\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[USenglish]{babel} 
\usepackage[super]{nth}
\usepackage[strict,autostyle]{csquotes} 
\usepackage[final, tracking=true, kerning=true]{microtype} \usepackage{tabto}
\usepackage{array, tabularx, graphicx, fancyhdr, soul, hyperref, geometry, enumitem, datetime}
\usepackage[style=iso]{datetime2}
\usepackage[symbol]{footmisc}

\geometry{
    letterpaper,
    left=1.5cm,
    right=1.5cm,
    top=2cm,
    bottom=2cm
 }
 
\setlength{\parindent}{0pt}

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define space between list items
\newcommand{\listitemspace}{0.25em}


\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

%% NAME
\def\name{Nicholas Osaka}
\def\lastname{Osaka}

\hypersetup{
    colorlinks      = true,
    urlcolor        = blue,
    citecolor       = black,
    linkcolor       = black,
}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}

\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{Curriculum Vitae}
\fancyhead[R]{last revised \today}
\fancyfoot{}
\fancyfoot[C]{\lastname~\thepage}

\raggedright{}
% name
\huge{\textbf{\name}}
\normalsize

% affiliation & contact
\vspace{.75em}
\begin{minipage}[t]{0.700\textwidth}
    Data Platform Engineer @ The Hartford\\
    Master's Student in Ethics and Applied Philosophy @ UNC Charlotte\\
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
    \flushright{}
    nosaka@charlotte.edu\\
    +1 (704) 649-1783\\
    nosaka.xyz
\end{minipage}

\noindent\rule{\textwidth}{.5pt}

% education
\section*{\normalsize{EDUCATION}}
\renewcommand{\arraystretch}{1.35}

\hspace{-1em}
\begin{tabularx}{\textwidth}{
    %  >{\raggedright\arraybackslash}p{11em}
    %  >{\raggedright\arraybackslash\hsize=1.97\hsize\linewidth=\hsize}X
    %  >{\raggedleft\arraybackslash\hsize=0.03\hsize\linewidth=\hsize}X }
     >{\raggedright\arraybackslash}p{3em}
     >{\raggedright\arraybackslash\hsize=1.97\hsize\linewidth=\hsize}X
     >{\raggedleft\arraybackslash\hsize=0.03\hsize\linewidth=\hsize}X }

    \textbf{M.A.} & Ethics and Applied Philosophy (in progress) with a graduate certificate in Gender, Sexuality, and Women's Studies, University of North Carolina at Charlotte & 2024\\
    \textbf{B.A.} & Philosophy (\textit{summa cum laude}), University of North Carolina at Charlotte & 2022\\
    \textbf{B.S.} & Computer Science (\textit{summa cum laude}) with a minor in Mathematics, University of North Carolina at Charlotte & 2022
\end{tabularx}

% industry experience
\section*{\normalsize{EXPERIENCE}}
\subsection*{\normalsize{The Hartford}}
% internship, ldp rotations
\subsection*{\normalisze{UNC Charlotte}}
% ta for 1212, 3155, 4111/5111, 3162
% REU w dr lipford

% presentations
\section*{\normalsize{PRESENTATIONS}}
\subsection*{\normalsize{Conference Presentations (Refereed)}}
\begin{tablist}
    \item[Future] \tab{}\enquote{Troubling the Metaverse: Disabled Phenomenologies and Feminist Critique} at the \nth{17} meeting of \textit{philo}SOPHIA: a feminist society. Mount Royal University, Calgary. March 14--17, 2024.
    \item[] \tab{}\enquote{A Bootstrapping Problem for Web3 Adoption} at the \nth{6} Transatlantic Conference on the Ethics of Business, Trade, \& Global Governance: Ethics and Sustainability in Banking and Finance. St.~Andrews, Scotland. November 23, 2023. [Joint presentation with Violet Victoria].
    \item[2023] \tab{}\enquote{Why a Socialist Cryptocurrency Can Never Exist: The Hermeneutical Resources of Virtual Money and Cryptocurrency} at the \nth{61} Meeting of the Society for Phenomenology and Existential Philosophy [Friday individual paper session]. Toronto Metropolitan University, Ontario. October 13.
    \item[] \tab{}\enquote{Feminist Practices of the Nikkei: Japanese Diasporic Feminisms Between and Across Generations} at the \nth{16} meeting of \textit{philo}SOPHIA: a feminist society. UNC Charlotte, NC. June 2.
    \item[] \tab{}\enquote{Japanese Anarcha-Feminism through the SeitÅ Literary Magazine} at Marquette University's Annual Graduate Philosophy Conference on Hidden Figures. Marquette University, WI. March 24.
    \item[2022] \tab{}\enquote{Japanese Ethical Philosophy and Algorithm Design} at the \nth{22} Annual Southern Appalachian Undergraduate Philosophy Conference. UNC Asheville, NC. April 16.
\end{tablist}
\subsection*{\normalsize{Workshop Presentations}}
\begin{tablist}
    \item[2023] \tab{}\enquote{Non-Fungible Tokens and Neoliberal Asset Logics/Economies via the Metaverse} at the Digital Worlds Workshop. University of Texas at Rio Grande Valley, Virtual. April 23.
\end{tablist}
\subsection*{\normalsize{Guest Lectures}}
\begin{tablist}
    \item[2023] \tab{}\enquote{Problematizing Classification Systems and Methods: Historical Sketches and Illustrations.} Lecture in Aileen Benedict's Introduction to Data Mining class, University of North Carolina at Charlotte. October 6. [Invited]
    \item[2022] \tab{}\enquote{Problems in Computer Vision Classification.} Lecture in Aileen Benedict's Introduction to Data Mining class, University of North Carolina at Charlotte. October 5. [Invited]
\end{tablist}

% public philosophy
\section*{\normalsize{PUBLIC PHILOSOPHY}}
\begin{tablist}
    \item[2023] \tab{}\enquote{\href{https://blog.apaonline.org/2023/07/05/naming-and-muddling-messiness-as-pedagogy/}{Naming and Muddling: Messiness as Pedagogy}.} Blog of the American Philosophical Association, Graduate Student Reflection Series. July 5. [Invited]
\end{tablist}

% service
\section*{\normalsize{SERVICE}}
\subsection*{\normalsize{Profession}}
\hspace{-.85em}
\begin{tabularx}{\textwidth}{
     >{\raggedright\arraybackslash}p{6.25em}
     >{\raggedright\arraybackslash}X}
    2023 -- Present & Organizer for the 2024 Ethics and Applied Philosophy Graduate Conference\\
    2022 -- 2023 & Disability and Accessibility Committee, \textit{philo}SOPHIA: a feminist society\\
    2022 -- 2023 & Organizer, Panel Moderator, and Reviewer for the 2023 Annual Ethics and Applied Philosophy Graduate Conference\\
    2022 & Reviewer for the 2022 Ethics and Applied Philosophy Graduate Conference
\end{tabularx}
\subsection*{\normalsize{Extracurricular University}}
\hspace{-.85em}
\begin{tabularx}{\textwidth}{
    >{\raggedright\arraybackslash}p{6.25em}
    >{\raggedright\arraybackslash}X}
   2023 -- Present & Co-President, Philosophical Union of UNC Charlotte\\
   2022 -- 2023 & Treasurer, Philosophical Union of UNC Charlotte\\
\end{tabularx}


% awards and grants
\section*{\normalsize{AWARDS, HONORS, AND GRANTS}}

\hspace{-0.85em}
\begin{tabularx}{1.014\textwidth}{
     >{\raggedright\arraybackslash}p{2.5em}
     >{\raggedright\arraybackslash\hsize=1.875\hsize\linewidth=\hsize}X
     >{\raggedright\arraybackslash\hsize=0.125\hsize\linewidth=\hsize}X }
    \multicolumn{2}{l}{\textit{Internal \textemdash{} UNC Charlotte}}\\
    2023 & Center for Professional \& Applied Ethics, Conference Travel Funding & \$750\\
    2023 & Graduate and Professional Student Government, Conference Travel Funding & \$500\\
    2020 & Atkins Library Undergraduate Research Award & \$1000\\

    \multicolumn{2}{l}{\textit{Internal \textemdash{} The Hartford}}\\
    2023 & Technology, Data Analytics, and Cybersecurity (TDAC) Triumph Award Finalist\\

    \textit{External}\\
    2022 & Prize for Paper Presentation, \nth{22} Annual Southern Appalachian Undergraduate Philosophy Conference & \$100\\

\end{tabularx}

% professional memberships
\section*{\normalsize{PROFESSIONAL MEMBERSHIPS}}
\begin{itemize}
    \item Society for Phenomenology and Existential Philosophy
    \item American Philosophical Association
    \item \textit{philo}SOPHIA: society for continental feminism
    \item Society for Philosophy and Disability
    \item Association for Computing Machinery \textemdash{} Special Interest Group on Accessible Computing (ACM SIGACCESS)
\end{itemize}

% certifications
\section*{\normalsize{CERTIFICATIONS}}
\begin{itemize}
    \item Amazon Web Services Certified Cloud Practitioner
    \item CITI Program IRB Members Certification
    \item CITI Program Social and Behavioral Sciences: Responsible Conduct of Research Certification
    \item CITI Program Engineering: Responsible Conduct of Research Certification
\end{itemize}

\end{document}
