\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[USenglish]{babel} 
\usepackage[super]{nth}
\usepackage{datetime}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage[strict,autostyle]{csquotes} 
\usepackage[final, tracking=true, kerning=true]{microtype} \usepackage{tabto}
\usepackage{hyperref}
\usepackage{soul}
\usepackage[style=iso]{datetime2}
\usepackage{fancyhdr}


\geometry{
    letterpaper,
    left=1.5cm,
    right=1.5cm,
    top=2cm,
    bottom=2cm
 }
 
\pagenumbering{gobble}
\setlength{\parindent}{0pt}

\hypersetup{
    colorlinks  = true,
    urlcolor    = blue,
    citecolor   = black,
    linkcolor   = blue,
    pdfauthor   = {Nicholas Osaka},
    pdftitle    = {Nicholas Osaka: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define space between list items
\newcommand{\listitemspace}{0.25em}


\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

\fancypagestyle{firstpage}
{
    \fancyhead[L]{Curriculum Vitae}
    \fancyhead[R]{last revised \today}
}

\begin{document}
\thispagestyle{firstpage}
\raggedright{}
% name
\huge{\textbf{Nicholas Osaka}}
\normalsize

% affiliation & contact
\vspace{.75em}
\begin{minipage}[t]{0.700\textwidth}
    Master's Student in Ethics and Applied Philosophy\\
    Department of Philosophy \\
    University of North Carolina at Charlotte
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
    \flushright{}
    % \href{mailto:nosaka@charlotte.edu}{nosaka@charlotte.edu} \\
    nosaka@charlotte.edu\\
    +1 (704) 649-1783\\
    % \href{https://nosaka.xyz}{nosaka.xyz}
    nosaka.xyz
\end{minipage}

% education
\section*{\normalsize{\MakeUppercase{Education}}}
\begin{tablist}
    \item[M.A.]  \tab{}Ethics and Applied Philosophy (in progress), University of North Carolina at Charlotte, 2024.\newline{}Graduate Certificate in Gender, Sexuality, and Women's Studies.
    \item[B.A.]  \tab{}Philosophy (\textit{summa cum laude}), University of North Carolina at Charlotte, 2022.
    \item[B.S.]  \tab{}Computer Science (Mathematics Minor, \textit{summa cum laude}), University of North Carolina at Charlotte, 2022.
\end{tablist}


% presentations
\section*{\normalsize{\MakeUppercase{Presentations}}}
\subsection*{\normalsize{Conference Presentations (Refereed)}}
\begin{tablist}
    \item[2023] \tab{}\enquote{Why a Socialist Cryptocurrency Can Never Exist} at the \nth{61} Meeting of the Society for Phenomenology and Existential Philosophy [Friday individual paper session]. Toronto Metropolitan University, Ontario. October 13.
    \item[2023] \tab{}\enquote{Feminist Practices of the Nikkei: Japanese Diasporic Feminisms Between and Across Generations} at the \nth{16} meeting of \textit{philo}SOPHIA: a feminist society. UNC Charlotte, NC. June 2.
    \item[2023] \tab{}\enquote{Japanese Anarcha-Feminism through the Seitō Literary Magazine} at Marquette University's Annual Graduate Philosophy Conference on Hidden Figures. Marquette University, WI. March 24.
    \item[2022] \tab{}\enquote{Japanese Ethical Philosophy and Algorithm Design} at the \nth{22} Annual Southern Appalachian Undergraduate Philosophy Conference. UNC Asheville, NC. April 16.
\end{tablist}
\subsection*{\normalsize{Workshop Presentations}}
\begin{tablist}
    \item[2023] \tab{}\enquote{Non-Fungible Tokens and Neoliberal Asset Logics/Economies via the Metaverse} at the Digital Worlds Workshop. University of Texas at Rio Grande Valley, Virtual. April 23.
\end{tablist}
\subsection*{\normalsize{Guest Lectures}}
\begin{tablist}
    \item[2023] \tab{}\enquote{Problematizing Classification Systems and Methods: Historical Sketches and Illustrations.} Lecture in Aileen Benedict's Introduction to Data Mining class, University of North Carolina at Charlotte. October 6. [Invited]
    \item[2022] \tab{}\enquote{Problems in Computer Vision Classification.} Lecture in Aileen Benedict's Introduction to Data Mining class, University of North Carolina at Charlotte. October 5. [Invited]
\end{tablist}

% public philosophy
\section*{\normalsize{\MakeUppercase{Public Philosophy}}}
\begin{tablist}
    \item[2023] \tab{}\enquote{\href{https://blog.apaonline.org/2023/07/05/naming-and-muddling-messiness-as-pedagogy/}{Naming and Muddling: Messiness as Pedagogy}.} Blog of the American Philosophical Association, Graduate Student Reflection Series. July 5. [Invited]
\end{tablist}

% service
\section*{\normalsize{\MakeUppercase{Service}}}
\subsection*{\normalsize{Profession}}
\begin{tablist}
    \item[2023-2024] \tab{}Organizer for the 2024 Ethics and Applied Philosophy Graduate Conference
    \item[2022-2023] \tab{}Organizer, Panel Moderator, and Reviewer for the 2023 Annual Ethics and Applied Philosophy Graduate Conference
    \item[2022-2023] \tab{}Disability and Accessibility Committee, \nth{16} meeting of \textit{philo}SOPHIA: a feminist society 
    \item[2022] \tab{}Reviewer for the 2022 Ethics and Applied Philosophy Graduate Conference
\end{tablist}
\subsection*{\normalsize{Extracurricular University}}
\begin{tablist}
    \item[2023-2024] \tab{}Co-President, Philosophical Union of UNC Charlotte
    \item[2022-2023] \tab{}Treasurer, Philosophical Union of UNC Charlotte
\end{tablist}

% honors and awards
\section*{\normalsize{\MakeUppercase{Selected Awards}}}
\begin{tablist}
    \item[2022] \tab{}Award for Paper Presentation, \nth{22} Annual Southern Appalachian Undergraduate Philosophy Conference
    \item[2020] \tab{}Atkins Library Undergraduate Research Award
\end{tablist}

% professional memberships
\section*{\normalsize{\MakeUppercase{Professional Memberships}}}
\begin{itemize}
    \item Society for Phenomenology and Existential Philosophy
    \item American Philosophical Association
    \item \textit{philo}SOPHIA: society for continental feminism
    \item Society for Philosophy and Disability
    \item Association for Computing Machinery \textemdash{} Special Interest Group on Accessible Computing (ACM SIGACCESS)
\end{itemize}

% certifications
\section*{\normalsize{\MakeUppercase{Certifications}}}
\begin{itemize}
    \item Amazon Web Services Certified Cloud Practitioner
    \item CITI Program IRB Members Certification
    \item CITI Program Social and Behavioral Sciences: Responsible Conduct of Research Certification
    \item CITI Program Engineering: Responsible Conduct of Research Certification
\end{itemize}

\end{document}
